R Notebook

### 2019-10-28 src/plots for paper.Rmd
minor plot changes plus some additions...

now just mak

>>>>

now create a table to see how many cells there are >0.5 in each month

```{r count cells >0.5}

binaryprob_list <- list.files("../output/maxent/paper_plots/hotspot_mapping/", pattern = ".*_bin_0.5_2d.asc", full.names = TRUE)
sum2d <- setNames(data.frame(matrix(ncol = 2, nrow = binl)), c("month", "count"))

for (r in 1:length(binaryprob_list)){
  ras <- raster(binaryprob_list[r])
  rnm <- names(ras)
  sum2d$month[r] <- gsub("_bin_0.5_2d", "", x = rnm)
  sum2d$count[r] <- cellStats(ras, sum, asSample = TRUE)
}

#order table from march to december
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
sum2d <- sum2d[match(mthord, sum2d$month), ]

#get proportion
tcs <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE) #file showing how many cells per depth
tcs <- tcs[-c(1:3), ] #because the top three rows are deeper than the capelin obs...
totc <- sum(tcs$no_cells)

for (r in 1:nrow(sum2d)){
  sum2d$proportion[r] <- (sum2d$count[r]/totc)
}

write.csv(sum2d, "../output/maxent/paper_plots/cell_count_0.5.csv", row.names = FALSE)

### 2019-10-28 src/testing_file.Rmd
minor plot changes plus some additions...

```{r}
dec <- read.csv("../output/maxent/models/decavgAIC.csv", header = TRUE)
colnames(dec)

our_summary1 <- list("Training AUC" = list("min" = ~ min(dec$train_AUC),
            "max" = ~ max(dec$train_AUC),
            "mean (sd)" = ~ qwraps2::mean_sd(dec$train_AUC),
       "Displacement" =
       list("min" = ~ min(.data$disp),
            "median" = ~ median(.data$disp),
            "max" = ~ max(.data$disp),
            "mean (sd)" = ~ qwraps2::mean_sd(.data$disp)),
       "Weight (1000 lbs)" =
       list("min" = ~ min(.data$wt),
            "max" = ~ max(.data$wt),
            "mean (sd)" = ~ qwraps2::mean_sd(.data$wt)),
       "Forward Gears" =
       list("Three" = ~ qwraps2::n_perc0(.data$gear == 3),
            "Four"  = ~ qwraps2::n_perc0(.data$gear == 4),
            "Five"  = ~ qwraps2::n_perc0(.data$gear == 5))
       )
```

>>>>

forget it... quickly done in excel

```{r}
library(qwraps2)

dec <- read.csv("../output/maxent/models/decavgAIC.csv", header = TRUE)

our_summary1 <- list("Training AUC" = list("min" = ~ min(.data$train_AUC),
            "max" = ~ max(.data$train_AUC),
            "mean (sd)" = ~ qwraps2::mean_sd(.data$train_AUC)),
       "Test AUC" =
       list("min" = ~ min(.data$test_AUC),
            "median" = ~ median(.data$test_AUC),
            "max" = ~ max(.data$test_AUC),
            "mean (sd)" = ~ qwraps2::mean_sd(.data$test_AUC))
       )

whole <-  summary_table(dec, our_summary1)
whole

dec <- read.csv("../output/maxent/models/decavgAIC.csv", header = TRUE)
summary(dec)
```

#no cells >0.5 per month

binaryprob_list <- list.files("../output/maxent/paper_plots/hotspot_mapping/", pattern = ".*_bin_0.5_2d.asc", full.names = TRUE)
sum2d <- setNames(data.frame(matrix(ncol = 2, nrow = binl)), c("month", "count"))

for (r in 1:length(binaryprob_list)){
  ras <- raster(binaryprob_list[r])
  rnm <- names(ras)
  sum2d$month[r] <- gsub("_bin_0.5_2d", "", x = rnm)
  sum2d$count[r] <- cellStats(ras, sum, asSample = TRUE)
}

#order table from march to december
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
sum2d <- sum2d[match(mthord, sum2d$month), ]

#get proportion
tcs <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE) #file showing how many cells per depth
tcs <- tcs[-c(1:3), ] #because the top three rows are deeper than the capelin obs...
totc <- sum(tcs$no_cells)

for (r in 1:nrow(sum2d)){
  sum2d$proportion[r] <- (sum2d$count[r]/totc)
}

write.csv(sum2d, "../output/maxent/paper_plots/cell_count_0.5.csv", row.names = FALSE)

# and get it as a proportion of habitat maybe....
